---
title: "ASSIGNMENT-6"
author: "RUTHRESHWARAN M"
date: "2023-05-04"
---

```{r}
library(haven)

datatibble1 <- read_sav("Raw/chap7data.sav")
datatibble1

freq_table <- table(datatibble1$bstrateg)
freq_table

library(psych)
describe(datatibble1$bstrateg)
summary(datatibble1$bstrateg)

prop.table(freq_table)

label1 <- c("yes","no")

pie(freq_table, label1, main="Pie Chart: Strategy",col = rainbow(length(freq_table)))

```

Dependent Variable:

```{r}
freq_table1 <- table(datatibble1$catestw1)
freq_table1


describe(datatibble1$catestw1)
summary(datatibble1$catestw1)

prop.table(freq_table1)

label2 <- c("manageial", "non-managerial", "no tests conducted")

pie(freq_table1, label2, main="Pie Chart: Strategy",col = rainbow(length(freq_table1)))

```

Chi-Square Test:

```{r}
df1 <- as.data.frame(datatibble1)
chisq.test(df1$bstrateg,df1$catestw1)
```

Alternative Nonparametric Test: Mann-Whitney Test Two category nominal independent variable (just like a t-test) and ordinal dependent variable that can be non-normally distributed.Is there a significant difference in outcomes across these two groups?

It is especially useful when the sample size is small. Instead of calculating mean scores, Mann whitney calculates the rank-ordering and comparison of scores. The bigger the difference in rank-ordering between the two groups or samples, the more likely the difference is statistically significant.

```{r}
summary(datatibble1$prp)
summary(datatibble1$antiunion)

describe(datatibble1$prp)
describe(datatibble1$antiunion)

freq_table2 <- table(datatibble1$prp)
freq_table2

library(ggplot2)

barplot.default(freq_table2)

freq_table3 <- table(datatibble1$antiunion)
freq_table3

barplot(freq_table3)
res <- wilcox.test(df1$antiunion ~ df1$prp, data = df1)
res
```

\`\`\`{r}
